Verifying Android Applications using Java PathFinder

### 2012-07-16 Papers/paper.tex
Adding paper updated intro and background

Although Android mobile applications and Java desktop applications both use the Java language, they are developed for a completely different
platforms.  and both contain many similar errors and defects. These defects include faults such as concurrency issues and run-time
exceptions. 
         are  compared to

The testing of Android applications  also faces many challenges including:
\begin{enumerate}
 \item The device challenge. 
 Mobile applications can only fully run on a mobile devices/emulators. Additionally the physical devices are
not designed with testing in mind.

 \item Event driven architecture.
 The event input must be simulated which is especially difficult due to the many types of
sensory inputs that must be supported.

 \item Operating system variety. It is impossible to test the application on all the different operating system versions.
\end{enumerate}

Due to these challenges and the rapid pace at which applications are developed and released, application testing becomes too expensive in
terms of time and money. This results in many mobile applications being unstable and unreliable.

Manual testing is not the solution to the problem as it is very expensive, time consuming and does not detect enough errors in
Android applications. That is why only automatic testing frameworks are the best options.

There are currently two ways to automatically test Android applications:
\begin{enumerate}
 \item testing on a physical device/emulator
  Install application on the device. Install test project that runs in the same process. The test project drives the application testing.

 %\begin{figure}[h!]
 %\centering
 %\includegraphics{../../Pictures/test_framework.png}
 % test_framework.png: 473x517 pixel, 96dpi, 12.51x13.68 cm, bb=0 0 355 388
%\end{figure}
  Examples include: Robotium\ref{} Android Test project

  MoneyRunner~\ref{},SPark~\ref{}
  -advantage wifi and many sensor events  already modelled
-problem is that emulator run actual android so testing framework as to either be android application
-

 \item testing the application on a computer
   Examples:
    android unit tests
    android lint

   mock objects
   adapt for pc
- static analysis or model android framework
- mock unit tests - still have to write the tests
- Robolectric
\end{enumerate}

% what are we going to do and why (WHAT ARE ADVANTAGES)
This paper describes jpf-android, an extension to Java PathFinder that allows the automatic testing of Android Applications.

@@

\newpage
\section{Background}
\subsection{The Android architecture}
Android is an open source software stack for mobile devices such as smartphones and tablets with an advanced RISC Machine (ARM)
architecture.

@@

One of the advantages of extending JPF is that it has been thoroughly tested and already works for Java applications. So as soon as the the
Android applications can run on JPF, common errors and defects can be detected.

@@

%what do I want to detect?

The objective of this project is to create a JPF extension based on JPF-AWT's scripting mechanism that will:
\begin{itemize}
 \item model the Android framework libraries using Java SE. Android applications are built on a framework written in Apache Harmony's Java
implementation. This framework will basically be simplified and closed down to allow the Android application to execute in a controlled
environment of JPF on a computer.

@@

\end{itemize}
\newpage
\section{Development}
% what are the issues of modelling the framework?
size of android framework - what to model
  - we don't necessarily want to have to run android applications exactly as they are run, then gets to complication to test all application
  paths.

   - the more is modelled the more has to be re-modelled if something changes

   - if too little is modelled, then support to little functionality

native code and the fact that it is run in different thread - but if not native cannot be back tracked

>>>>

%Although Android mobile applications and Java desktop applications both use the Java language, they are developed for completely different
%platforms.  and both contain many similar errors and defects. These defects include faults such as concurrency issues and run-time
%exceptions. 
 %        are  compared to

%Software testing is a complex and time consuming process.

Android applications and Java desktop applications are designed for completely different computing platforms. They are both however, built on an implementation of the 
Java programming language. As a consequence, Android applications contain many of the same defects as Java applications. These defects include but is not limited to concurrency
issues and runtime exceptions. It follows that it must be possible to adapt existing testing frameworks for Java applications to verify Android applications.

The problem is that Android applications face the following obstacles when it comes to application testing:
\begin{description}
 \item [Event driven architecture]. Android application flow is driven by events. This event input must be simulated which is especially difficult due to the many types of
sensory and system inputs that must be supported.

 \item [The device challenge]. 
 Mobile applications are created to run on ARM devices/ emulators. Additionally the physical devices are
not designed with testing in mind. Alternative ways have to be devised to automatically simulate input to the application.
- java version

 \item [Operating system variety]. It is impossible to test an application on all the different operating system versions.
\end{description}

Due to these challenges and the rapid pace at which applications are developed and released~\cite{}, mobile application testing becomes too expensive in
terms of time and money. This results in many mobile applications being unstable and unreliable.

Manual testing is not the solution to the problem as it is very expensive, time consuming and does not detect enough errors in
Android applications. That is why only automatic testing frameworks are discussed below.

There are currently two ways to automatically test Android applications: on the device/emulator or on a computer.

The most common way is to test an application is the on a physical device/emulator. Examples of such projects include 
the Android testing framework~\cite{AndroidTesting}, MonkeyRunner~\cite{AndroidTesting} and Robotium~\cite{Robotium}. 
These projects depend on Android's built-in JUnit framework and InstrumentationTestRunner as the test case runner~\cite{AndroidTesting}.Other
projects use alternative ways to automatically generate input by manipulating the accessibility technologies 
or the software keyboard~\cite{AccessibilityTech, KeyboardModel}. Mockito or Android Mock a user to  mock out the Android SDK. While this is a valid approach, we have found that without Robolectric, the level of mocking needed to test an 
Android app quickly yields tests that are essentially reverse implementations of the application code.

The advantage of running the application on the emulator is that the application runs on actual android operating system. The disadvantage is, as mentioned before,
Android applications are driven by user and system events. So the input has to be modeled which is not so easy. It is slow to run the tests and each test 
sequence has to be defined and executed one by one.

The other approach is to test an Android application on the computer. There are different ways of implementing such a framework. Android lint~\cite{} for example makes 
use of static analysis to identify common errors in applications. Robolectric~\cite{} create mocks of classes that allows an application to be Unit tested on the JVM.

% what are we going to do and why (WHAT ARE ADVANTAGES)
This paper describes jpf-android, an extension to Java PathFinder~\cite{JPFDocs} which is a Java application model checker framework. jpf-android will allow the automatic
verification of Android Applications on the standard Java jvm.

@@

\section{Background}
\subsection{The Android architecture}
Android is an open source software stack for mobile devices such as smartphones and tablets with an advanced RISC Machine (ARM)
architecture.

@@

One of the advantages of extending JPF is that it has been thoroughly tested and already works for Java applications. So as soon as the the
Android applications can run on JPF, common errors and defects can be detected. It provides an simple way to model classes.

@@

%what do I want to detect?
The objective of this project is to create a JPF extension based on JPF-AWT's scripting mechanism that will:
\begin{itemize}
 \item model the Android framework libraries using Java SE. Android applications are built on a framework written in Apache Harmony's Java
implementation. This framework will basically be simplified and closed down to allow the Android application to execute in a controlled
environment of JPF on a computer.

@@

\end{itemize}
\newpage
\section{Development}

% what are the issues of modelling the framework?
Modeling the Android framework is quite a complex task. The main problems being:
\begin{itemize}
 \item android.jar libs
\item we need a driver 
 \item size of android framework - what to model
  - we don't necessarily want to have to run android applications exactly as they are run, then gets to complication to test all application
  paths.
   - the more is modelled the more has to be re-modelled if something changes
   - if too little is modelled, then support to little functionality

\item native code and the fact that it is run in different thread - but if not native cannot be back tracked

\end{itemize}
